The first high-redshift changing-look quasars

### 2020-07-10 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
Big CIV MBH, Lbol, eta update

{\bf In Table~\ref{tab:Eddington_ratios} we report the \civ\ Virial
masses calculated using equation~\ref{eqn:virial_masses}, the measured
luminosites and FWHM from QSFit and the
\citet{VestergaardPeterson2006} calibrations.} \citet{Shen2011} and
\citet{Kozlowski2017} report virial black hole masses based on \mgii\
and \civ\ for the SDSS/BOSS observations of our targets. For
J1205+3422 (and MJD 53498), \citet{Shen2011} report $\log (M_{\rm BH, MgII}/M_{\odot})
= 9.55 \pm 0.05$ and $\log(M_{\rm BH, CIV}/M_{\odot}) = 9.49 \pm
0.04$.

We use the mean of five values --- three from our three epochs
and two from \citet{Shen2011} --- to calculate an adopted SMBH mass of
$\log (M_{\rm BH, vir}/M_{\odot}) = 9.73$ for J1205+3422.  J1638+2827
also has two virial mass measurements from \citet{Shen2011}, as well
as two measurements from \citet{Kozlowski2017}. The mean mass
measurement adopted for J1638+2827 is $\log(M_{\rm BH, vir}/M_{\odot}
= 9.09$. For J2228+2201, there are two \citet{Kozlowski2017}
measurements, leading to a mean adopted mass of $\log(M_{\rm BH,
vir}/M_{\odot} = 9.37$. We use these mean SMBH masses when calculating
the Eddington ratios.

From the virial mass estimates, all our objects have SMBH masses
$M_{\rm BH} >10^{9} M_{\odot}$.  This is at the upper end of SMBH
masses at all epochs, and towards the extreme of the mass distribution
for $z\sim2$ quasars.  Figure~\ref{fig:CIV_MBHvsREW} compares the
\civ\ EW versus the virial SMBH masses for our multi-epoch
observations to a sample of $\approx$20,000 $z>1.5$ SDSS quasars from
the QSFit catalog \citep{Calderone2017}.

{\bf The values in Table~\ref{tab:QSFit-results} are
$\approx$0.27-0.30 dex higher than the estimates in
Table~\label{tab:Eddington_ratios}, which is to be expected given the
difference of calibrations factors. In fact, the virial products are
all remarkably constant and compatible with a single black hole mass
estimate, within the standard 0.5 dex uncertainty, across the 3 epochs
for all the quasars.  This fact gives us confidence in the line
fitting methods.}

@@

\begin{table}
  \centering
  \begin{tabular}{l l  cc    l     r}
    \hline
    \hline
\multirow{2}{*}{Object} & \multirow{2}{*}{MJD} & \multicolumn{2}{c}{$\log (M/M_{\odot})$} & log($L_{\rm bol}$) &  \multirow{2}{*}{$\eta_{\rm Edd}$}  \\
                                    &                                  &    QSFit               &   Liter. value               &                             &    \\
    \hline
                                    & 53498                        &    9.39                &  9.49$\pm$0.04$^{\dagger}$   &   47.22                  &  $-$0.61   \\
 J1205+3422               & 58538                         &    9.78               &   ---                                        &  46.07                  &   $-$1.76 \\  %% L_Edd (J12)  = 47.82637   for log(M) = 9.726
                                    & 58693                        &    9.38               &   ---                                               &  46.57                &  $-$1.26  \\                    
    \hline 
                                    & 54553                        &   8.84                &  8.74$\pm$0.15$\dagger$                     & 46.17   & $-$1.03  \\
J1638+2827                 & 55832                       &    8.80                &    9.13$^{\ddagger}$                                         & 45.98   & $-$1.21  \\      %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
                                    & 58583                        &   9.01                &  ---                         & 46.50   & $-$0.69   \\
    \hline 
                                     & 56189                       & 8.70                 & 8.73$^{\ddagger}$                         & 46.23  &  $-$1.24 \\
J2228+2201                 & 56960                       &  9.39                &   ---                       & 47.34  & $-$0.12  \\      %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
                                     & 58693                      &  8.97                    &    ---                      & 46.83   &  $-$0.64 \\
    \hline
    \hline
  \end{tabular}
  \caption{Virial Mass estimates, bolometric luminosities and Eddington ratios for the
    three quasars. 
    $\dagger$From the \citet{Shen2011} SDSS DR7 Quasar catalog.
    $\ddagger$From the \citet{Kozlowski2017} SDSS-III BOSS DR12 quasar catalog.
%    are given in either \citet{Shen2011} or    \citet{Kozlowski2017} for the three CLQs.
    We scale these values using
    our measured $\nu L_{\nu}$ continuum luminosity values.  From
    Section~\ref{sec:BH_masses}, we assume: $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.726$ for J1205+3422; $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.091$ for J1638+2827, and $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.366$ for J2228+2201.  The Eddington luminosity
    $L_{\rm Edd} = 1.26\times10^{38} (M_{\rm BH}/M_{\odot})$ erg s$^{-1}$
    and $\eta_{\rm Edd}$ is the log of the Eddington ratio.}
\label{tab:Eddington_ratios} 
\end{table}

>>>>

{\bf In Table~\ref{tab:Eddington_ratios} we report the \civ\ virial
  masses calculated using the measured
luminosites and FWHM from QSFit, equation~\ref{eqn:virial_masses} and the
\citet{VestergaardPeterson2006} calibrations.} \citet{Shen2011} and
\citet{Kozlowski2017} report virial black hole masses based on \mgii\
and \civ\ for the SDSS/BOSS observations of our targets. For
J1205+3422 (and MJD 53498), \citet{Shen2011} report $\log (M_{\rm BH, MgII}/M_{\odot})
= 9.55 \pm 0.05$ and $\log(M_{\rm BH, CIV}/M_{\odot}) = 9.49 \pm
0.04$, while for J1638+2827 (MJD 54553) \citet{Shen2011} report 
$\log (M_{\rm BH, MgII}/M_{\odot}) = 9.03 \pm 0.37$ and
$\log(M_{\rm BH, CIV}/M_{\odot}) = 8.74 \pm 0.15$.

{\bf The values in Table~\ref{tab:QSFit-results} are
$\approx$0.3 dex higher than the estimates in
Table~\ref{tab:Eddington_ratios}, which is to be expected given the
difference of calibrations factors. In fact, the virial products are
all remarkably constant and compatible with a single black hole mass
estimate, within the standard 0.5 dex uncertainty, across the 3 epochs
for all the quasars.  This fact gives us confidence in the line
fitting methods.}

From the virial mass estimates, all our objects have SMBH masses $M_{\rm BH} >10^{9} M_{\odot}$.  This is at the upper end of SMBH masses at all epochs, and towards the extreme of the mass distribution for $z\sim2$ quasars.  Figure~\ref{fig:CIV_MBHvsREW} compares the luminosity \civ\ EW versus the virial SMBH masses for our multi-epoch 
observations to a sample of $\approx$20,000 $z>1.5$ SDSS quasars from
the QSFit catalog \citep{Calderone2017}.

{\bf With the black hole masses in hand, we can calculate the Eddington luminosities of 
the three quasars. To be consistent with 
For the Bolometric luminosity, $L_{\rm Bol}$, \citet{Shen2011} and 
\citet{Kozlowski2017} use the bolometric corrections of BC$_{1350}$ = 3.81 
from the composite spectral energy distribution (SED) in \citet{Richards2006b}.

We report the black hole \civ\ virial masses, the bolometric luminosities
and the Eddington ratios ($\eta=\log(L_{}/L_{Edd})$ in Table~\ref{tab:Eddington_ratios}. 
}

%We use the mean of five values --- three from our three epochs and two from \citet{Shen2011} --- to calculate an adopted SMBH mass of $\log (M_{\rm BH, vir}/M_{\odot}) = 9.73$ for J1205+3422.  J1638+2827 also has two virial mass measurements from \citet{Shen2011}, as well as two measurements from \citet{Kozlowski2017}. The mean mass measurement adopted for J1638+2827 is $\log(M_{\rm BH, vir}/M_{\odot} = 9.09$. For J2228+2201, there are two \citet{Kozlowski2017} measurements, leading to a mean adopted mass of $\log(M_{\rm BH, vir}/M_{\odot} = 9.37$. We use these mean SMBH masses when calculating the Eddington ratios.

@@

%%
%%  These values are generated using the 
%%
\begin{table}
  \centering
  \begin{tabular}{l l  cc         r}
    \hline
    \hline
                      &                  &                                      &                              & \\
Object            & MJD           &  $\log (M/M_{\odot})$  & log($L_{\rm bol}$)  &  $\eta_{\rm Edd}$  \\
                      &                  &                                      &                              & \\
    \hline
                      & $^{\dagger }$53498  &  9.49              &  47.22                  &  -0.378   \\
                      & 53498                      &    9.39            &                    &  $-$0.61   \\
 J1205+3422 & 58538                       &    9.78           &                      &   $-$1.76 \\  
                     & 58693                         &    9.38          &                   &  $-$1.26  \\                    
    \hline
                     & $^{\dagger }$54553    &  8.74            &  46.17   & $-$0.677  \\
                     & 54553                         &   8.84                 &             & $-$1.03  \\
J1638+2827  & $^{\ddagger }$55832  &    9.13                  & 45.98   & $-$1.21  \\      
                      & 55832                        &   8.80                  & 45.98   & $-$1.21  \\     
                      & 58583                        &   9.01                  & 46.50   & $-$0.69   \\
    \hline
                         & $^{\ddagger }$56189   & 8.73                  & 46.23  &  $-$1.24 \\
                         & 56189                         & 8.70                  & 46.23  &  $-$1.24 \\
J2228+2201     & 56960                          &  9.39               & 47.34  & $-$0.12  \\      
                         & 58693                         &  8.97               & 46.83   &  $-$0.64 \\
    \hline
    \hline
  \end{tabular}
  \caption{Virial Mass estimates, bolometric luminosities and Eddington ratios for the
    three quasars. 
    $\dagger$From the \citet{Shen2011} SDSS DR7 Quasar catalog.
    $\ddagger$From the \citet{Kozlowski2017} SDSS-III BOSS DR12 quasar catalog.
%    are given in either \citet{Shen2011} or    \citet{Kozlowski2017} for the three CLQs.
    We scale these values using
    our measured $\nu L_{\nu}$ continuum luminosity values.  From
    Section~\ref{sec:BH_masses}, we assume: $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.726$ for J1205+3422; $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.091$ for J1638+2827, and $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.366$ for J2228+2201.  The Eddington luminosity
    $L_{\rm Edd} = 1.26\times10^{38} (M_{\rm BH}/M_{\odot})$ erg s$^{-1}$
    and $\eta_{\rm Edd}$ is the log of the Eddington ratio.}
\label{tab:Eddington_ratios} 
\end{table}
